---
title: "Quick Overview on Cars"
author: "Gadil ShivaPuthra"
date: "07/11/2020"
output: 
    slidy_presentation: default
    ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## *Introduction of the dataset mtcars*

This dataset contains the data of cars with variables such as no. of cylinders, miles per gallon, weight of the car, gear type, engine arrangement, swept volume etc.

The presentation will consist of, A scatter plot with 'mpg' i.e, miles per gallon on Y-axis and 'cyl' i.e, no.of cylinders on the X-axis to determine the effect on mileage of a car based on no.of cylinders.

## *Getting the data into R and showing a brief summary*

```{r}
data("mtcars")

head(mtcars, n= 15)
```

## *A plot indicating the effect which we all know already which is the more the no.of cylinders the faster the car is and the faster cars have lesser mileage *

Here mpg =  mileage in miles per gallon 
and  cyl =  no.of cylinders in the car.
```{r}
library(plotly)
plot_ly(mtcars, x = ~mpg, y = ~cyl, 
        type = "scatter", mode = "markers", color = ~'blue')
```